\LARGE \bf Analysis of the effectiveness of recursive networks in the classification task

### 2019-06-04 paper/main.tex
paper: abstract update

Recurrent Neural Networks are class of models designed to process sequences. Most of the typical fields of applications include natural language processing, handwriting recognition and generation, or text, music or images generation. In this work emphasis was put on ReNet architecture designed to solve image classification task. Modification based on Hilbert Curve was introduced to ReNet and obtained accuracy was very close to results obtained for original ReNet network. Modification also provided significant training time reduction. We compared ReNet networks to convolutional networks and found that the latter proved to be superior.

>>>>

Recurrent Neural Networks are class of models designed to process sequences. Most of typical fields of applications include natural language processing, recognition of handwriting and generation of text, music or images. In this work emphasis was put on a ReNet architecture designed to solve an image classification task. A modification based on a Hilbert curve was introduced to the ReNet and obtained accuracy was very close to results acquired for the original ReNet network. The modification also provided significant training time reduction for some datasets. Comparison of ReNet networks to convolutional networks proved that the latter are superior.
